Stable Neo-Hookean Flesh Simulation

### 2019-09-27 LaTeX-Master-Vorlage/chapter/Background.tex
working on structure in Energy
working working doing stuff

\section{Notation and Convention}

\subsection{General Notation}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics and additionally we will include the declarations in the paper \textit{Stable Neo-Hookean Flesh Simulation}. 
\\
Scalars are represented by regular, normal-weight variables whereas 
tensors and matrices are represented by upper-case bold letters. Vectors will be denoted by bold lower-case variables.

\subsection{Tensor Notation}

Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}. They decided to to define vectorization vec(.) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012):

\[
\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad vec(\textbf{A}) = \boldsymbol{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
\]

@@

Additionally we well have to deal with $4^{th}$ order tensors in the following matrix-of-matrices form:

@@

These matrices are denoted by using blackboard bold.

TODO: 2nd order matrix, see paper 4.1 Tensor Notation

@@

>>>>

\section{Notation and Convention}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics taken from \cite{Spencer1980}. Additionally we will include the declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation}.

\subsection{General Notation}
Scalars are represented by regular, normal-weight variables such as $a$ whereas 
tensors and matrices are represented by upper-case bold letters as for example $\textbf{A}$. Vectors will be denoted by bold lower-case variables like $\textbf{a}$.

\subsection{Tensor Notation}
Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}. They decided to to define vectorization vec(.) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.

\[
\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\textbf{A}) = \boldsymbol{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
\]

@@

Additionally we will have to deal with $4^{th}$ order tensors in the following form of matrix-of-matrices:

@@

These matrices are denoted by using blackboard bold.
\\
If we now vectorize $\mathbb{A}$ we receive the following form:

\[
\mathbb{A} = \operatorname{vec}(\mathbb{A})=\left[\operatorname{vec}\left(\mathrm{A}_{00}\right)\left|\operatorname{vec}\left(\mathrm{A}_{10}\right)\right| \operatorname{vec}\left(\mathrm{A}_{01}\right) | \operatorname{vec}\left(\mathrm{A}_{11}\right)\right]
=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right]=\boldsymbol{\check{A}}
\]

The advantage of this form is that we can write several expressions as a cross product which we will need later.

@@

To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor

### 2019-09-27 LaTeX-Master-Vorlage/main.tex
working on chapter Paper, a lot to do, a lot of confusion, starting with structure
working working doing stuff

\pagenumbering{arabic}
\input{chapter/Einleitung} \clearpage
\input{chapter/Background} \clearpage
\input{chapter/Beispiele} \clearpage
\input{chapter/paper} \clearpage

@@

\printbibliography[heading=bibintoc, keyword={book}, title={Literaturverzeichnis}]\clearpage
\printbibliography[heading=bibintoc, keyword={online}, title={Onlinequellen}]\clearpage
\printbibliography[heading=bibintoc, keyword={image}, title={Bildquellen}]\clearpage

>>>>

\pagenumbering{arabic}
\input{chapter/Einleitung} \clearpage
\input{chapter/Background} \clearpage
%\input{chapter/Beispiele} \clearpage
\input{chapter/Paper} \clearpage

@@

\printbibliography[heading=bibintoc, keyword={book}, title={Literature}]\clearpage
\printbibliography[heading=bibintoc, keyword={article}, title={Articles}]\clearpage
\printbibliography[heading=bibintoc, keyword={online}, title={Online Resources}]\clearpage
\printbibliography[heading=bibintoc, type=misc,title={Various References}] \clearpage
\printbibliography[heading=bibintoc, keyword={image}, title={Images Resources}]\clearpage
